---
title: "Grammar of Graphics Midterm Paper"
author: Ryan Lalicker
date: today
date-format: long
abstract: |
  WRITE ABSTRACT BEFORE SUBMITTING  (@test)
execute: 
  echo: false
  warning: false
columns: 2
format:
  pdf:
    fig-align: center
    fig-width: 6
    fig-height: 4
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

```{r}
#| label: fig-set-up
#| echo: false
#| eval: true

# Add all necessary libraries here.


# Datasets used.

```

```{r}
#| label: fig-scratch-work
#| echo: false
#| eval: false

# Any work done in R that should not be ran as part of the paper can go here.
## EX: How many unique entires in a dataset.


```


# Introduction


The accompanying files to this project can be found [here](https://github.com/RyanLalicker/STAT-892-Final), or by reaching out to me.


# Motivation

# Literary Review

# Experimental Methods

# Data Collection

# Analysis Plan

# Conclusion


\newpage

# References

::: {#refs}
:::

\newpage

# Appendix A: R Code

```{r}
#| label: appendix-A
#| echo: true
#| eval: false



```
\newpage

# Appendix B: AI Prompts and Answers

**Prompt:** How many R's are in the word strawberry?

**Answer:** The word strawberry contains three R's.