---
title: "STAT 892 - Final Paper"
author: Ryan Lalicker
date: today
date-format: long
abstract: |
  WRITE ABSTRACT BEFORE SUBMITTING  (@test) (@lauer)
execute: 
  echo: false
  warning: false
columns: 2
format:
  pdf:
    fig-align: center
    fig-width: 6
    fig-height: 4
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

```{r}
#| label: fig-set-up
#| echo: false
#| eval: true

# Add all necessary libraries here.


# Datasets used.

```

```{r}
#| label: fig-scratch-work
#| echo: false
#| eval: false

# Any work done in R that should not be ran as part of the paper can go here.
## EX: How many unique entires in a dataset.


```


# Introduction

Many areas of research rely on visualizations to express data and to give a general audience an overview of the topic without making them suffer through an academic paper over an area they have little to no experience in.  This applies to other areas of life as well such as news, entertainment, and public health that  reach the largest audience possible with easily-digestible visualizations and quick explanations over in-depth, domain specific reports. 
**Get CITATION**
Although this practice goes back many centuries (@firstplot), in today's fast moving technology driven world expressing information through visualizations has never been easier.  Yet, visualizations need to be effective in order to have the desired outcome of educating the public.




This leads




The accompanying files to this project can be found [here](https://github.com/RyanLalicker/STAT-892-Final), or by reaching out to me.


# Motivation

# Literary Review

In 

# Experimental Methods

# Data Collection

# Analysis Plan

# Conclusion


\newpage

# References

::: {#refs}
:::

\newpage

# Appendix A: R Code

```{r}
#| label: appendix-A
#| echo: true
#| eval: false



```
\newpage

# Appendix B: AI Prompts and Answers

**Prompt:** How many R's are in the word strawberry?

**Answer:** The word strawberry contains three R's.