---
title: "Plots Used for STAT 892 Experiment"
author: Ryan Lalicker
execute: 
  echo: false
  warning: false
columns: 2
format:
  pdf:
    fig-align: center
    fig-width: 6
    fig-height: 4
editor: 
  markdown: 
    wrap: sentence
---

```{r}
#| label: fig-set-up
#| echo: false
#| eval: true

library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)

```

# Introduction

This document is contains the plots that will (or could) be used in the experiment for the STAT 892 final paper.  For more information on this experiment see the project's [GitHub page](https://github.com/RyanLalicker/STAT-892-Final).


# Noncontroversial Plots

## Bar Graphs

```{r,,fig.pos="H"}
#| label: fig-bar-NC1
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

RubberDucks <- data.frame(
  Year = c("2018", "2023"),
  Sales = c(12000, 13500)
)

ggplot(RubberDucks, aes(x = Year, y = Sales)) +
  geom_bar(stat = "identity", color = "skyblue", fill = "skyblue", width = 0.7) + coord_cartesian(ylim = c(0, 15000)) +
  labs(title = "Ticket Sales for the Rockford Peaches Baseball Team",
       x = "Year",
       y = "Ticket Sales") +
  theme_minimal() + theme(panel.grid = element_blank())

ggplot(RubberDucks, aes(x = Year, y = Sales)) +
  geom_bar(stat = "identity", color = "skyblue", fill = "skyblue", width=0.7) + coord_cartesian(ylim = c(11500, 14000)) +
  labs(title = "Ticket Sales for the Rockford Peaches baseball Team",
       x = "Year",
       y = "Ticket Sales") +
  theme_minimal() + theme(panel.grid = element_blank())
```

**Question:** How large was the increase in ticket sales from 2018 to 2023?

```{r,,fig.pos="H"}
#| label: fig-bar-NC2
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

shakes <- data.frame(
  Year = c("January", "July"),
  Sold = c(3000, 3450)
)

ggplot(shakes, aes(x = Year, y = Sold)) +
  geom_bar(stat = "identity", color = "skyblue", fill = "skyblue", width = 0.7) + coord_cartesian(ylim = c(0, 5000)) +
  labs(title = "Number of Milk Shakes Sold per month at NYC Store",
       x = "Month",
       y = "Milk Shakes Sold") +
  theme_minimal() + theme(panel.grid = element_blank())

ggplot(shakes, aes(x = Year, y = Sold)) +
  geom_bar(stat = "identity", color = "skyblue", fill = "skyblue", width = 0.7) + coord_cartesian(ylim = c(2800, 3500)) +
  labs(title = "Number of Milk Shakes Sold per month at NYC Store",
       x = "Month",
       y = "Milk Shakes Sold") +
  theme_minimal() + theme(panel.grid = element_blank())


```

**Question:**

## Pie Charts

```{r,,fig.pos="H"}
#| label: fig-pie-NC1
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

control_movies <- data.frame(
  Genre = c("Action", 
            "Romance",
            "Thriller", 
            "Sci-Fi", 
            "Western", 
            "Epic"),
  Percentage = c(28, 23, 22, 
                 13, 10, 4)
)

deceptive_movies <- data.frame(
  Genre = c("Action", 
            "Romance",
            "Thriller", 
            "Sci-Fi", 
            "Western", 
            "Epic"),
  Percentage = c(35, 29, 27, 
                 5, 3, 1)
)

pie(control_movies$Percentage, 
    labels = paste(control_movies$Genre, 
                   " (", control_movies$Percentage, "%)", sep = ""), 
    main = "Type of Movies by Acme Studios",
    col = topo.colors(nrow(control_movies)))

pie(deceptive_movies$Percentage, 
    labels = paste(deceptive_movies$Genre, 
                   " (", control_movies$Percentage, "%)", sep = ""), 
    main = "Type of Movies by Acme Studios",
    col = topo.colors(nrow(deceptive_movies)))


```


**Question:** How many more romance movies were made than westerns?


```{r,,fig.pos="H"}
#| label: fig-pie-NC2
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```

**Question:**

```{r,,fig.pos="H"}
#| label: fig-line-NC1
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

## Line Graphs


box_office <- data.frame(
  Year = c("2006", "2007",
           "2008", "2009",
           "2010", "2011",
           "2012", "2013",
           "2014", "2015", "2016"),
  Dollars = c(9.2, 9.6,
              9.5, 10.5,
              10.6, 10.2,
              10.8, 10.9,
              10.4, 11.1,
              11.4)
)

ggplot(box_office, aes(x = Year, y = Dollars, group = 1)) +
  geom_line(color = "dodgerblue2", size = 1) +  
  geom_text(aes(label = Dollars), 
            vjust = -0.5, size = 4, color = "black") + 
  labs(title = "Box Office Revenue for Acme Studios",
       x = "Year",
       y = "Revenue (in billions of dollars)") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  ylim(0, 13) + 
  theme(panel.grid = element_blank())

ggplot(box_office, aes(x = Year, y = Dollars, group = 1)) +
  geom_line(color = "dodgerblue2", size = 1) +  
  geom_text(aes(label = Dollars), 
            vjust = -0.5, size = 4, color = "black") + 
  labs(title = "Box Office Revenue for Acme Studios",
       x = "Year",
       y = "Revenue (in billions of dollars)") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  ylim(9, 11.6) + 
  theme(panel.grid = element_blank())

```


**Question:**


```{r,,fig.pos="H"}
#| label: fig-line-NC2
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```

**Question:**


# Controversial Plots

## Bar Graphs

```{r,,fig.pos="H"}
#| label: fig-bar-Con1
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```

**Question:**

**Lean:**

```{r,,fig.pos="H"}
#| label: fig-bar-Con1
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```

**Question:**

**Lean:**

## Pie Charts

```{r,,fig.pos="H"}
#| label: fig-pie-Con1
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```

**Question:**

**Lean:**

```{r,,fig.pos="H"}
#| label: fig-pie-Con2
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```


**Question:**

**Lean:**

## Line Graphs

```{r,,fig.pos="H"}
#| label: fig-line-Con1
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```

**Question:**

**Lean:**

```{r,,fig.pos="H"}
#| label: fig-line-Con2
#| echo: false
#| eval: true
#| fig-cap: ""
#| layout-ncol: 2
#| fig-subcap: 
#|  - "Control"
#|  - "Deceptive"
#| fig-width: 6
#| fig-height: 4

```

**Question:**

**Lean:**

\newpage

# R Code Used

## Libraries Used

```{r}
#| echo: true
#| eval: false

library(ggplot2)

```

## Noncontroversial Plots

### Bar Graphs

```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

RubberDucks <- data.frame(
  Year = c("2018", "2023"),
  Sales = c(12000, 13500)
)

ggplot(RubberDucks, aes(x = Year, y = Sales)) +
  geom_bar(stat = "identity", color = "skyblue", fill = "skyblue", width = 0.7) 
+ coord_cartesian(ylim = c(0, 15000)) +
  labs(title = "Ticket Sales for the Rockford Peaches baseball Team",
       x = "Year",
       y = "Ticket Sales") +
  theme_minimal() + theme(panel.grid = element_blank())

ggplot(RubberDucks, aes(x = Year, y = Sales)) +
  geom_bar(stat = "identity", color = "skyblue", fill = "skyblue", width=0.7) 
+ coord_cartesian(ylim = c(11500, 14000)) +
  labs(title = "Ticket Sales for the Rockford Peaches baseball Team",
       x = "Year",
       y = "Ticket Sales") +
  theme_minimal() + theme(panel.grid = element_blank())
```



```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-subcap: 
#| fig-width: 6
#| fig-height: 4


```



### Pie Charts

```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

control_movies <- data.frame(
  Genre = c("Action", 
            "Romance",
            "Thriller", 
            "Sci-Fi", 
            "Western", 
            "Epic"),
  Percentage = c(28, 23, 22, 
                 13, 10, 4)
)

deceptive_movies <- data.frame(
  Genre = c("Action", 
            "Romance",
            "Thriller", 
            "Sci-Fi", 
            "Western", 
            "Epic"),
  Percentage = c(35, 29, 27, 
                 5, 3, 1)
)

pie(control_movies$Percentage, 
    labels = paste(control_movies$Genre, 
                   " (", control_movies$Percentage, "%)", sep = ""), 
    main = "Type of Movies by Acme Studios",
    col = topo.colors(nrow(control_movies)))

pie(deceptive_movies$Percentage, 
    labels = paste(deceptive_movies$Genre, 
                   " (", control_movies$Percentage, "%)", sep = ""), 
    main = "Type of Movies by Acme Studios",
    col = topo.colors(nrow(deceptive_movies)))


```



```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```

### Line Graphs 

```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4


box_office <- data.frame(
  Year = c("2006", "2007",
           "2008", "2009",
           "2010", "2011",
           "2012", "2013",
           "2014", "2015", "2016"),
  Dollars = c(9.2, 9.6,
              9.5, 10.5,
              10.6, 10.2,
              10.8, 10.9,
              10.4, 11.1,
              11.4)
)

ggplot(box_office, aes(x = Year, y = Dollars, group = 1)) +
  geom_line(color = "dodgerblue2", size = 1) +  
  geom_text(aes(label = Dollars), 
            vjust = -0.5, size = 4, color = "black") + 
  labs(title = "Box Office Revenue for Acme Studios",
       x = "Year",
       y = "Revenue (in billions of dollars)") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  ylim(0, 13) + 
  theme(panel.grid = element_blank())

ggplot(box_office, aes(x = Year, y = Dollars, group = 1)) +
  geom_line(color = "dodgerblue2", size = 1) +  
  geom_text(aes(label = Dollars), 
            vjust = -0.5, size = 4, color = "black") + 
  labs(title = "Box Office Revenue for Acme Studios",
       x = "Year",
       y = "Revenue (in billions of dollars)") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  ylim(9, 11.6) + 
  theme(panel.grid = element_blank())

```



```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```



## Controversial Plots

### Bar Graphs

```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```



```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```



### Pie Charts

```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```


```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```


### Line Graphs

```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```

```{r,,fig.pos="H"}
#| echo: true
#| eval: false
#| layout-ncol: 2
#| fig-width: 6
#| fig-height: 4

```
